Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
merge

library(tidyverse)
library(arrow)
library(dplyr)
```

@@

```{r}
#| include: false
#| warning: false
#| message: false
trump_data<-trump_data |>mutate(candidate="Trump")
harris_data<-harris_data|>mutate(candidat="Harris")
combined_data_total<-bind_rows(harris_data,trump_data)
combined_data_total<-combined_data_total|>
  mutate(
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight
  ) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| tbl-colwidths: [45,15]
#| tbl-cap: "Summary of the Linear Regression Model for Predicting Polling Outcomes"
#| layout-ncol: 2
#| label: tbl-summary
modelsummary::msummary(
  list(
    "Harris Unweighted" = harris_unweighted_model, 
    "Harris Weighted" = harris_weighted_model,
    "Trump Unweighted" = trump_unweighted_model,
    "Trump Weighted" = trump_weighted_model
  ))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
####### Prediction and Plot ######
set.seed(233)
####### Prediction for Harris ######
new_data_harris <- data.frame(
  end_date = seq(
    min(harris_data$end_date),
    max(harris_data$end_date),
    length.out = 2000
  ),
  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$pollster)), 
  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$population)),
  sample_size = sample(1:2300, size = 2000, replace = TRUE)
)|>
  mutate(
    national_poll = if_else(state == "National", 1, 0),
    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight,
    candidate="Harris"
  )

####### Prediction for Trump ######
new_data_trump <- data.frame(
  end_date = seq(
    min(trump_data$end_date),
    max(trump_data$end_date),
    length.out = 2000
  ),
  pollster = factor(sample(levels(trump_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$pollster)),
 population= factor(sample(levels(trump_data$population), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$population)),
   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$state)),  
  sample_size =sample(1:2300, size = 2000, replace = TRUE),
  pollster_quality= sample(2:4, size = 2000, replace = TRUE)
)|>
  mutate(
   national_poll = if_else(state == "National", 1, 0),
      recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),  
    combined_weight = recency_weight * sample_size_weight,
    candidate="Trump"
  )
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-trend
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

# Plotting with the filtered data
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-respondent
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

>>>>

library(tidyverse)
library(arrow)
library(dplyr)
library(ggplot2)
```

@@

```{r}
#| include: false
#| warning: false
#| message: false
combined_data_total<-bind_rows(harris_data,trump_data)
combined_data_total<-combined_data_total|>
  mutate(
    candidate = candidate_name,
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight
  ) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| tbl-cap: "Summary of the Linear Regression Model for Predicting Harris' Voting Outcomes by polling results"
#| label: tbl-summary1
modelsummary::msummary(
  list(
    "Harris Unweighted" = harris_unweighted_model, 
    "Harris Weighted" = harris_weighted_model
  ), 
  options = list("longtable" = TRUE))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| tbl-cap: "Summary of the Linear Regression Model for Predicting Trump's Voting Outcomes by polling results"
#| label: tbl-summary2
modelsummary::msummary(
  list(
    "Trump Unweighted" = trump_unweighted_model,
    "Trump Weighted" = trump_weighted_model
  ), 
  options = list("longtable" = TRUE))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
####### Prediction and Plot ######
set.seed(233)
####### Prediction for Harris ######
new_data_harris <- data.frame(
  end_date = seq(
    min(harris_data$end_date),
    max(harris_data$end_date),
    length.out = 2000
  ),
  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$pollster)), 
  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$population)),
  sample_size = sample(1:2300, size = 2000, replace = TRUE)
)|>
  mutate(
    national_poll = if_else(state == "National", 1, 0),
    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight,
    candidate="Kamala Harris"
  )

####### Prediction for Trump ######
new_data_trump <- data.frame(
  end_date = seq(
    min(trump_data$end_date),
    max(trump_data$end_date),
    length.out = 2000
  ),
  pollster = factor(sample(levels(trump_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$pollster)),
 population= factor(sample(levels(trump_data$population), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$population)),
   state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE), 
                    levels = levels(trump_data$state)),  
  sample_size =sample(1:2300, size = 2000, replace = TRUE),
  pollster_quality= sample(2:4, size = 2000, replace = TRUE)
)|>
  mutate(
   national_poll = if_else(state == "National", 1, 0),
      recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),  
    combined_weight = recency_weight * sample_size_weight,
    candidate="Donald Trump"
  )
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using unweighted fitted Linear Model"
#| label: fig-support-trend1
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump using weighted fitted Linear Model"
#| label: fig-support-trend2
# Plotting with the filtered data
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Unweighted Fitted Linear Model"
#| label: fig-support-respondent1
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Weighted Fitted Linear Model"
#| label: fig-support-respondent2
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Weighted Fitted Linear Model"
#| label: fig-support-state2
## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```
